Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-04-30 RNARedPrint-Bioinfo2018.tex
Edit Fig 2 caption

%To reduce the cost of the precomputation, we used a stacking energy model 
%as a proxy for the Turner model. Indeed, we observed a strong linear 
%dependency between the Turner energy and the 
%emphasize that only the simple stacking energies are directly targeted
%(at $\pm$10\% tolerance, except for a few hard instances). Due to our
%linear adjustment, we finally achieve well-controlled energies in the
%realistic Turner energy model.
\begin{figure*}[t]
  \begin{center}
    {\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset}\hspace{.5cm}
    {\sf \bfseries B}\includegraphicstop[width=0.57\textwidth]{Figs/energy_distribution}
  \end{center}
  \caption{%
  	Targeting specific energies using multi-dimensional Boltzmann sampling. 
  	(A) Accuracy of targeting over all target structures of the \Software{Modena} benchmark instances \texttt{RNAtabupath} (2str), \texttt{3str} and \texttt{4str}. Shown is the relative deviation of targeted and achieved energies in the simple stacking model and the Turner model.
  	(B) Turner energy distributions for three target structures (right) while targeting $(-40,-40,-20)$ and $(-20,-20,-20)$ free energy vectors. For comparison, we show the distribution of uniform and Boltzmann samples; respectively associated with homogenous weights $1$ (uniform) and $e^\beta$ (Boltzmann). 
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
}
  \label{fig:energydist}
\end{figure*}
\subsection{Generating high-quality seeds for further optimization}
We empirically study the capacity of \ourprog{} to improve the generation of seed sequences for subsequent local optimizations, showing an important application in biologically relevant scenarii.

>>>>

%To reduce the cost of the precomputation, we used a stacking energy model 
%as a proxy for the Turner model. Indeed, we observed a strong linear 
%dependency between the Turner energy and the 
%emphasize that only the simple stacking energies are directly targeted
%(at $\pm$10\% tolerance, except for a few hard instances). Due to our
%linear adjustment, we finally achieve well-controlled energies in the
%realistic Turner energy model.
\begin{figure*}[t]
  \begin{center}
    {\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset}\hspace{.5cm}
    {\sf \bfseries B}\includegraphicstop[width=0.57\textwidth]{Figs/energy_distribution}
  \end{center}
  \caption{%
    Targeting specific energies using multi-dimensional Boltzmann
    sampling.  (A) Accuracy of targeting over all target structures of
    the \Software{Modena} benchmark instances \texttt{RNAtabupath}
    (2str), \texttt{3str} and \texttt{4str}. Shown is the relative
    deviation of targeted and achieved energies in the simple stacking
    model and the Turner model.  (B) Turner energy distributions for
    three target structures S1, S2 and S3. We show the results of
    targeting the respective free energies $(-40,-40,-20)$ and
    $(-20,-20,-20)$ for the target structures (annotated in red and
    blue, resepectively)---this demonstrates the
    effectivity of our adaptive multi-dimensional Boltzmann sampling
    procedure; moreover, for comparison, the distributions for uniform
    (U) and Boltzmann (B) samples---respectively associated with
    homogenous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
      }
  \label{fig:energydist}
\end{figure*}
\subsection{Generating high-quality seeds for further optimization}
We empirically study the capacity of \ourprog{} to improve the generation of seed sequences for subsequent local optimizations, showing an important application in biologically relevant scenarii.
